Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-17 MUSES_vs_BYOD_solutions.tex
Couple of errors and forgot to add changed .bib

It is important to note that MUSES does not work as an antivirus itself, but has a sensor which checks if the device has already an antivirus, and raises a security violation alert if not. It might happen then that the user ignores this advice and the device becomes compromised. As it would be explained in the next section, the sensors are constantly sending their monitored values, and therefore patterns are created, soted, and processed on the server. In case the device gets infected with rootkit-type malware \cite{bickford2010rootkits}, a sudden change in the values of the sensors will be noticed by the server, which will immediately warn the user, and decrease the devide trust value.

@@

There are some other components, namely: the \textit{Security Policies/Risk Management} tool, that lets the company's CSO to define and manage Security Policies and Rules in a friendly way. It also lets the management of risk-related information, useful for the RT2AE process, such as the assets' values. The \textit{Privacy Enhancing System} which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system. There are three important points with relation to this matter \cite{deliverable72}. First, the data that the user provides to the system (such as name, or email) is only used for authentication purposes, so they are checked when the user logs in the system, but they are not used for Data Mining tasks. Then, the location of the device is never sent and stored in the database, but instead, there are a number of defined `zones'. What is checked is that the user is inside one of those zones of interest. For instance, a company might want to know if the user is inside or outside a zone defined as `company premises'. And finally, the use in MUSES of what is called as `soft limit' and `hard limit' \cite{deliverable72}. These limits exist to ensure the users that their data will not be kept longer than necessary. The soft limit is defined by the components that use the data (Event Processor, RT2AE, and Knowledge Refinement System) for decision making or rule refinement, but do not need that data anymore. In addition, the hard limit is provided by the law, in case that the employee leaves the company, or if there is a national law specifying a maximum data retention period.

>>>>

It is important to note that MUSES does not work as an antivirus itself, but has a sensor which checks if the device has already an antivirus, and raises a security violation alert if not. It might happen then that the user ignores this advice and the device becomes compromised. As it would be explained in the next section, the sensors are constantly sending their monitored values, and therefore patterns are created, stored, and processed on the server. In case the device gets infected with rootkit-type malware \cite{bickford2010rootkits}, a sudden change in the values of the sensors will be noticed by the server, which will immediately warn the user, and decrease the devide trust value.

@@

There are some other components, namely: the \textit{Security Policies/Risk Management} tool, that lets the company CSO to define and manage Security Policies and Rules in a friendly way. It also lets the management of risk-related information, useful for the RT2AE process, such as the assets' values. The \textit{Privacy Enhancing System} which is a module aimed to fit with the legal compliance of the system regarding the user's data anonymisation and retaining of these data in the system. There are three important points with relation to this matter \cite{deliverable72}. First, the data that the user provides to the system (such as name, or email) is only used for authentication purposes, so they are checked when the user logs in the system, but they are not used for Data Mining tasks. Then, the location of the device is never sent and stored in the database, but as was stated in the previous section, there are a number of defined `zones'. What is checked is that the user is inside one of those zones of interest. For instance, a company might want to know if the user is inside or outside a zone defined as `company premises'. And finally, the use in MUSES of what is called as `soft limit' and `hard limit' \cite{deliverable72}. These limits exist to ensure the users that their data will not be kept longer than necessary. The soft limit is defined by the components that use the data (Event Processor, RT2AE, and Knowledge Refinement System) for decision making or rule refinement, but do not need that data anymore. In addition, the hard limit is provided by the law, in case that the employee leaves the company, or if there is a national law specifying a maximum data retention period.
